PANCHANGE_data_preprocessing

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Amended key worker status chunk to work for all cohorts.

# Key worker status
```{r Key worker}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
#create numeric version of the variable
glad.employment.raw.id <- glad.employment.raw.id %>%
  mutate(
    key_worker_numeric =
      case_when(
        employment.government_work_key_workers_numeric == "0" ~ 0,
        employment.government_work_key_workers_numeric > 0 ~ 1
      )
    )

#recode the numeric version into a factor
glad.employment.raw.id <- glad.employment.raw.id %>%
  mutate(
    key_worker =
      recode_factor(
        key_worker_numeric,
        `0` = "No key worker",
        `1` = "Key worker"
        )
    )

glad.employment.raw.id %>%
  freq(key_worker)
}
```

>>>>

## Key worker status
```{r Key worker}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
#create numeric version of the variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    key_worker_numeric =
      case_when(
        employment.government_work_key_workers_numeric == "0" ~ 0,
        employment.government_work_key_workers_numeric > 0 ~ 1
      )
    )

#recode the numeric version into a factor
employment.raw.id <- employment.raw.id %>%
  mutate(
    key_worker =
      recode_factor(
        key_worker_numeric,
        `0` = "No key worker",
        `1` = "Key worker"
        )
    )

employment.raw.id %>%
  freq(key_worker)
}
```
